\documentclass{beamer}
\usetheme{Madrid}

\title{Advanced Features of Rust Programming}
\author{Paweł Nowak}
\date{\today}

\begin{document}

\maketitle

\section{Zero Cost Abstraction}
\begin{frame}{Zero Cost Abstraction}
\begin{itemize}
  \item Derived from C++ concept.
  \item Achieved through efficient iterators and other abstractions.
  \item Enables high performance without sacrificing safety or expressiveness.
\end{itemize}
\end{frame}

\section{Ownership Model}
\begin{frame}{Ownership Model}
\begin{itemize}
  \item Fundamental to Rust’s memory safety guarantees.
  \item Ownership rules:
    \begin{itemize}
      \item Each value in Rust has a single owner.
      \item Only one owner at a time.
      \item When the owner goes out of scope, the value is dropped.
    \end{itemize}
  \item Prevents common errors like dangling pointers and memory leaks.
\end{itemize}
\end{frame}

\section{Algebraic Data Types}
\begin{frame}{Algebraic Data Types}
\begin{itemize}
  \item Inspired by functional languages like Haskell.
  \item Combines different types in a single coherent unit.
  \item Commonly used with `enum` for defining custom data types.
\end{itemize}
\end{frame}

\section{Polymorphism}
\begin{frame}{Polymorphism}
\begin{itemize}
  \item Achieved in Rust through traits.
  \item Traits allow for shared behavior across different types.
  \item Similar to interfaces in other languages but more powerful.
\end{itemize}
\end{frame}

\section{Async Programming}
\begin{frame}{Async Programming}
\begin{itemize}
  \item Integral part of Rust for efficient IO operations.
  \item Uses `async` and `await` syntax for easy-to-read asynchronous code.
  \item Enables concurrent execution without the complexity of threads.
\end{itemize}
\end{frame}

\section{Macros}
\begin{frame}{Macros}
\begin{itemize}
  \item Macros in Rust are powerful and hygienic.
  \item Allow for metaprogramming and code generation.
  \item Hygienic nature ensures no unintended scope interference.
\end{itemize}
\end{frame}

\section{Cargo}
\begin{frame}{Cargo - The Rust Package Manager}
\begin{itemize}
  \item Cargo manages Rust projects, dependencies, and builds.
  \item Inspired by Node.js's npm.
  \item Simplifies project management and compilation process.
\end{itemize}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
\begin{itemize}
  \item Rust provides advanced features for safe, concurrent, and practical programming.
  \item Its unique approach to memory safety and management sets it apart.
  \item Continuously evolving with a strong focus on developer needs.
\end{itemize}
\end{frame}

\end{document}
